Domestic cooking and likelihood

### 2020-04-05 inst/cook.Rmd
more detail

\[
\frac{p_1+t}{p_1+t+p_2+p_3+p_4+p_5}\cdot
\frac{p_2  }{      p_2+p_3+p_4+p_5}\cdot
\frac{p_3  }{          p_3+p_4+p_5}\cdot
\frac{p_4  }{              p_4+p_5}\cdot
\frac{p_5  }{                  p_5}\cdot
\]

@@

\[
\frac{p_3  }{p_1+t+p_2+p_3+p_4+p_5}\cdot
\frac{p_1+t}{p_1+t+p_2+    p_4+p_5}\cdot
\frac{p_5  }{      p_2+    p_4+p_5}\cdot
\frac{p_2  }{      p_2+    p_4    }\cdot
\frac{p_4  }{              p_4    }\cdot
\]

@@

```{r}
Hafter <- rank_likelihood(1:5)+rank_likelihood(c(3,1,5,2,4))
pnames(Hafter) <- pnames(Hbefore)
Hafter %<>%  pwa("p1")
Hafter
```

@@

```{r}
pnames(Hbefore) <- c(pnames(Hbefore),"S")
maxp(Hbefore + Hafter)
```

The above suggesting that the training had a sizable effect; and we
may test the null that the training had no effect:

```{r}
specificp.gt.test(Hbefore + Hafter,"S",0)
```

>>>>

\[
\frac{p_1+S}{p_1+S+p_2+p_3+p_4+p_5}\cdot
\frac{p_2  }{      p_2+p_3+p_4+p_5}\cdot
\frac{p_3  }{          p_3+p_4+p_5}\cdot
\frac{p_4  }{              p_4+p_5}\cdot
\frac{p_5  }{                  p_5}\cdot
\]

@@

\[
\frac{p_3  }{p_1+S+p_2+p_3+p_4+p_5}\cdot
\frac{p_1+S}{p_1+S+p_2+    p_4+p_5}\cdot
\frac{p_5  }{      p_2+    p_4+p_5}\cdot
\frac{p_2  }{      p_2+    p_4    }\cdot
\frac{p_4  }{              p_4    }\cdot
\]

@@

```{r,usepwafortraining}
Hafter <- rank_likelihood(1:5)+rank_likelihood(c(3,1,5,2,4))
pnames(Hafter) <- pnames(Hbefore)
Hafter %<>%  pwa("p1")
Hafter
```

@@

```{r,addbeforeandafter}
pnames(Hbefore) <- c(pnames(Hbefore),"S")
maxp(Hbefore+Hafter)
```

[In the above, note the use of the overloaded "`+`", meaning to add
two likelihood functions for independent observations].  The evaluate
suggests that the training had a sizable effect; we may use
\code{specficp.gt.test()} to test a null of zero strength:

```{r,testnullzerotrainingeffect}
specificp.gt.test(Hbefore+Hafter, "S", 0)
```
